---
title: "Function Gallery: rajiveplus API Showcase"
author: "rajiveplus package authors"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Function Gallery: rajiveplus API Showcase}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  comment    = "#>",
  fig.width  = 7,
  fig.height = 5,
  message    = FALSE,
  warning    = FALSE
)
run_heavy <- FALSE   # set to TRUE once to regenerate all cached .rds files
data_dir  <- "data"
```

## Overview

This gallery showcases every exported user-facing function in **rajiveplus**
using a lightweight three-block simulation so all examples run quickly. For a
real-data application see `vignette("cll_application")`.

Each section follows the same structure:

> **Function name** – why you need it  
> *Code example*  
> *Interpretation: what to expect*

### Gallery Roadmap

| Category | Functions |
|---|---|
| Simulation | `ajive.data.sim` |
| Core decomposition | `Rajive` |
| S3 — *rajive* class | `print`, `summary` |
| Rank accessors | `get_joint_rank`, `get_individual_rank`, `get_all_ranks` |
| Component extractors | `get_joint_scores`, `get_block_scores`, `get_block_loadings`, `get_block_matrix` |
| Diagnostic extraction | `extract_components` (5 `what` modes) |
| Decomposition visualization | `data_heatmap`, `decomposition_heatmaps_robustH` |
| Variance explained | `showVarExplained_robust`, `plot_variance_explained` |
| Score plots | `plot_scores`, `plot_components` (`pairs`, `density`) |
| AJIVE diagnostic plots | `plot_components` (`rank_threshold`, `bound_distributions`, `ajive_diagnostic`) |
| Feature visualization | `plot_components` (`top_features`, `component_heatmap`) |
| S3 autoplot / fortify | `autoplot`, `fortify` |
| Feature ranking | `rank_features` (4 modes) + 3 wrappers |
| Association testing | `associate_components` (4 modes) + 3 wrappers; `plot_components` (`association`) |
| Stability | `assess_stability` (3 targets) + 2 wrappers; `plot_stability_heatmap`; `plot_components` (`stability`) |
| Summarization | `summarize_components` (6 `summary_type` values) |
| Jackstraw | `jackstraw_rajive`; `print`, `summary`, `autoplot`, `fortify`; `plot_jackstraw` (3 types); `plot_components` (`volcano`, `jackstraw_summary`); `get_significant_vars`; `summarize_significant_vars` |
| Reporting / export | `export_results`, `rajive_report` |

---

## Prerequisites

```{r setup}
library(rajiveplus)
library(ggplot2)
```

---

## Shared Simulated Data

```{r gallery-compute, eval = run_heavy}
# ===== Run once (run_heavy = TRUE) to generate the gallery cache =====
set.seed(2)
n   <- 80L
pks <- c(60L, 50L, 40L)

sim      <- ajive.data.sim(K = 3, rankJ = 2, rankA = c(5L, 4L, 4L),
                           n = n, pks = pks, dist.type = 1)
blocks   <- sim$sim_data
names(blocks) <- c("mRNA", "Methylation", "Proteomics")
for (k in seq_along(blocks))
  rownames(blocks[[k]]) <- paste0("sample", seq_len(n))

meta_df <- data.frame(
  group      = rep(c("A", "B"), each = n / 2L),
  score_cont = rnorm(n),
  time_event = abs(rnorm(n, mean = 5, sd = 2)),
  event_flag = rbinom(n, 1L, 0.6),
  row.names  = paste0("sample", seq_len(n)),
  stringsAsFactors = FALSE
)

fit <- Rajive(
  blocks               = blocks,
  initial_signal_ranks = c(5L, 4L, 4L),
  n_wedin_samples      = 200L,
  n_rand_dir_samples   = 200L
)

set.seed(42)
js <- jackstraw_rajive(fit, blocks, n_null = 5L, correction = "BH")

assoc_cat  <- associate_components(fit, meta_df, variable = "group",
                                   mode = "categorical")
assoc_cont <- associate_components(fit, meta_df, variable = "score_cont",
                                   mode = "continuous")

stab_rank <- assess_stability(fit, blocks, c(5L, 4L, 4L),
                              target = "joint_rank", B = 5L)
stab_load <- assess_stability(fit, blocks, c(5L, 4L, 4L),
                              target = "loadings",   B = 5L)
stab_comp <- assess_stability(fit, blocks, c(5L, 4L, 4L),
                              target = "components", B = 5L)

dir.create(data_dir, showWarnings = FALSE, recursive = TRUE)
saveRDS(
  list(blocks = blocks, meta = meta_df, fit = fit, js = js,
       assoc_cat = assoc_cat, assoc_cont = assoc_cont,
       stab_rank = stab_rank, stab_load = stab_load, stab_comp = stab_comp),
  file = file.path(data_dir, "gallery_precomp.rds")
)
```

```{r gallery-load}
# ===== Load cached results (always runs) =====
cache      <- readRDS(file.path(data_dir, "gallery_precomp.rds"))
blocks     <- cache$blocks
meta_df    <- cache$meta
fit        <- cache$fit
js         <- cache$js
assoc_cat  <- cache$assoc_cat
assoc_cont <- cache$assoc_cont
stab_rank  <- cache$stab_rank
stab_load  <- cache$stab_load
stab_comp  <- cache$stab_comp
```

---

# 1  Data Simulation

## `ajive.data.sim()`

Generates synthetic multi-block data with known joint and individual ranks.
Essential for testing and benchmarking: ground-truth decomposition structure
is accessible.

```{r sim-ajive-data-sim}
set.seed(7)
sim2 <- ajive.data.sim(
  K         = 2,
  rankJ     = 2,
  rankA     = c(4, 3),
  n         = 60,
  pks       = c(80, 60),
  dist.type = 1,
  noise     = 1
)
cat("True joint rank:      ", sim2$rankJ_true, "\n")
cat("True individual ranks:", sim2$rankA_true, "\n")
cat("Block 1 dimensions:   ", dim(sim2$sim_data[[1]]), "\n")
```

**Interpretation.** `sim_data` is a list of K matrices (samples x features).
`rankJ_true` and `rankA_true` record the planted ground-truth ranks for
benchmarking recovery performance.

---

# 2  Core Decomposition

## `Rajive()`

The main function. Decomposes each block into **joint** (shared), **individual**
(block-specific), and **noise** components using robust angle-based JIVE.

```{r core-rajive, eval = FALSE}
fit_demo <- Rajive(
  blocks               = blocks,
  initial_signal_ranks = c(5L, 4L, 4L),
  full                 = TRUE,
  n_wedin_samples      = 200L,
  n_rand_dir_samples   = 200L,
  joint_rank           = NA,
  num_cores            = 1L
)
```

**Interpretation.** Returns a `rajive` S3 object. Set `joint_rank = NA` for
automatic rank estimation. Increase `n_wedin_samples` for a more precise Wedin
bound. The `initial_signal_ranks` vector should be set conservatively above the
expected rank per block.

---

# 3  S3 Methods — `rajive` class

## `print.rajive()`

```{r s3-print}
print(fit)
```

**Interpretation.** Number of blocks, estimated joint rank, and individual rank
per block. A joint rank of 0 means no shared signal was detected.

---

## `summary.rajive()`

```{r s3-summary}
summary(fit)
```

**Interpretation.** Returns a tidy `data.frame` with one row per block showing
`joint_rank` and `individual_rank`. Use for inspection before extraction.

---

# 4  Rank Accessors

## `get_joint_rank()`

```{r rank-joint}
jrank <- get_joint_rank(fit)
cat("Estimated joint rank:", jrank, "\n")
```

---

## `get_individual_rank()`

```{r rank-indiv}
for (k in seq_along(blocks))
  cat(sprintf("Block %d (%s) individual rank: %d\n",
              k, names(blocks)[k], get_individual_rank(fit, k)))
```

---

## `get_all_ranks()`

```{r rank-all}
rank_tbl <- get_all_ranks(fit)
knitr::kable(rank_tbl, caption = "All block ranks")
```

**Interpretation.** Combines `get_joint_rank()` and per-block
`get_individual_rank()` into one data frame for reporting.

---

# 5  Component Extractors

## `get_joint_scores()`

```{r extract-joint-scores}
J_scores <- get_joint_scores(fit)
cat("Dimensions (samples x joint components):", dim(J_scores), "\n")
print(round(head(J_scores, 4), 3))
```

**Interpretation.** Each column is one joint factor; each row is one sample.
These are estimated quantities — downstream p-values do not account for score
estimation error (treat results as exploratory).

---

## `get_block_scores()`

```{r extract-block-scores}
bl1_joint  <- get_block_scores(fit, k = 1, type = "joint")
bl2_indiv  <- get_block_scores(fit, k = 2, type = "individual")
cat("Block 1 joint scores:", dim(bl1_joint), "\n")
cat("Block 2 individual scores:", dim(bl2_indiv), "\n")
```

---

## `get_block_loadings()`

```{r extract-block-loadings}
bl1_load <- get_block_loadings(fit, k = 1, type = "joint")
cat("Block 1 joint loadings (features x components):", dim(bl1_load), "\n")
```

**Interpretation.** High absolute loading → feature strongly associated with
the component. Use `jackstraw_rajive()` for formal significance rather than raw
loading magnitude.

---

## `get_block_matrix()`

```{r extract-block-matrix}
J1 <- get_block_matrix(fit, k = 1, type = "joint")
I1 <- get_block_matrix(fit, k = 1, type = "individual")
E1 <- get_block_matrix(fit, k = 1, type = "noise")
cat("Reconstruction error:", round(max(abs(blocks[[1]] - J1 - I1 - E1)), 6), "\n")
```

**Interpretation.** J + I + E ≈ original matrix. The joint matrix captures
shared cross-block structure; individual captures block-unique signal; noise is
the remainder.

---

# 6  Diagnostic Extraction

## `extract_components()` — `what = "rank_diagnostics"` (wide)

```{r diag-wide}
diag_wide <- extract_components(fit, what = "rank_diagnostics", format = "wide")
cat("Cutoff rule:", diag_wide$cutoff_rule, "\n")
cat("Wedin threshold:", round(diag_wide$wedin_cutoff, 4), "\n")
cat("Rand-dir threshold:", round(diag_wide$rand_cutoff, 4), "\n")
cat("Joint rank estimate:", diag_wide$joint_rank_estimate, "\n")
```

**Interpretation.** Overall threshold = `max(wedin_cutoff, rand_cutoff)` —
a practical heuristic, not a formal FWER/FDR guarantee.

---

## `extract_components()` — `what = "rank_diagnostics"` (long)

```{r diag-long}
diag_long <- extract_components(fit, what = "rank_diagnostics", format = "long")
knitr::kable(head(diag_long, 6),
             caption = "Rank diagnostics — long format (first 6 SVs)")
```

---

## `extract_components()` — `what = "scores"`

```{r diag-scores}
scores_long <- extract_components(fit, what = "scores", type = "joint",
                                  format = "long")
cat("Columns:", names(scores_long), "\n")
head(scores_long, 4)
```

---

## `extract_components()` — `what = "loadings"`

```{r diag-loadings}
load_long <- extract_components(fit, what = "loadings", type = "joint",
                                block = 1L, format = "long")
cat("Loadings dimensions:", dim(load_long), "\n")
head(load_long, 4)
```

---

## `extract_components()` — `what = "variance"`

```{r diag-variance}
var_df <- extract_components(fit, blocks = blocks, what = "variance")
knitr::kable(round(var_df, 3), caption = "Variance explained per block (%)")
```

---

# 7  Decomposition Visualization

## `data_heatmap()` — requires *reshape2*

```{r viz-data-heatmap, fig.height = 3}
if (requireNamespace("reshape2", quietly = TRUE)) {
  data_heatmap(
    data  = t(blocks[[1]][, 1:20]),
    title = "Block 1 (mRNA): first 20 features",
    xlab  = "Samples",
    ylab  = "Features"
  )
}
```

**Interpretation.** Color gradients reveal overall variation patterns.
Distinct bands across samples suggest latent structure.

---

## `decomposition_heatmaps_robustH()` — requires *cowplot* + *reshape2*

```{r viz-decomp-heatmaps, fig.height = 6}
if (requireNamespace("cowplot", quietly = TRUE) &&
    requireNamespace("reshape2", quietly = TRUE)) {
  decomposition_heatmaps_robustH(blocks = blocks, jive_results_robust = fit)
}
```

**Interpretation.** Four panels (original, joint, individual, noise). The joint
row should look structurally similar across all blocks; the noise row should
resemble random variation.

---

# 8  Variance Explained

## `showVarExplained_robust()`

```{r var-show}
var_list <- showVarExplained_robust(fit, blocks)
cat("Joint:     ", round(unlist(var_list$Joint), 3), "\n")
cat("Individual:", round(unlist(var_list$Indiv), 3), "\n")
cat("Residual:  ", round(unlist(var_list$Resid), 3), "\n")
```

---

## `plot_variance_explained()`

```{r var-plot, fig.height = 4}
plot_variance_explained(fit, blocks)
```

**Interpretation.** Stacked bars show joint (blue), individual (light blue),
and residual (red) proportions per block. Blocks with high joint proportion
are strongly integrated with the shared signal.

---

# 9  Score Plots

## `plot_scores()`

```{r scores-plot-scores, fig.height = 4}
jr <- get_joint_rank(fit)
if (jr >= 2) {
  plot_scores(fit, k = 1, type = "joint", comp_x = 1, comp_y = 2,
              group = meta_df$group)
} else {
  plot_scores(fit, k = 1, type = "joint", comp_x = 1,
              group = meta_df$group)
}
```

**Interpretation.** Separation of groups along an axis indicates the component
captures variation correlated with that grouping variable.

---

## `plot_components()` — `"pairs"`

```{r scores-pairs, fig.height = 5}
plot_components(fit, plot_type = "pairs", type = "joint",
                group = meta_df$group)
```

---

## `plot_components()` — `"density"`

```{r scores-density, fig.height = 4}
plot_components(fit, plot_type = "density", type = "joint",
                group = meta_df$group)
```

**Interpretation.** Bimodal densities suggest discrete structure; unimodal
indicates a continuous gradient.

---

# 10  AJIVE Diagnostic Plots

## `plot_components()` — `"rank_threshold"`

```{r diag-rank-threshold, fig.height = 4}
plot_components(fit, plot_type = "rank_threshold") +
  labs(subtitle = "Threshold = max(Wedin, random-direction) — heuristic, not FWER/FDR-controlled")
```

**Interpretation.** Squared singular values above the dashed line are
classified as joint. A clear elbow gap indicates stable rank estimation.

---

## `plot_components()` — `"bound_distributions"`

```{r diag-bound-dist, fig.height = 4}
plot_components(fit, plot_type = "bound_distributions")
```

**Interpretation.** Histograms of Wedin and random-direction bound samples.
A narrow distribution indicates a stable threshold.

---

## `plot_components()` — `"ajive_diagnostic"` — requires *patchwork*

```{r diag-ajive-full, fig.height = 7}
if (requireNamespace("patchwork", quietly = TRUE)) {
  plot_components(fit, plot_type = "ajive_diagnostic")
}
```

**Interpretation.** The composite first-look diagnostic. Review whether joint
components clearly exceed both cutoffs and whether bounds are well-separated.

---

# 11  Feature Visualization

## `plot_components()` — `"top_features"`

```{r feat-top, fig.height = 4}
plot_components(fit, plot_type = "top_features", type = "joint",
                block = 1L, component = 1L, top_n = 20L)
```

**Interpretation.** Features at the top drive joint variation most strongly.
Do not treat ranking alone as significance — use `jackstraw_rajive()`.

---

## `plot_components()` — `"component_heatmap"`

```{r feat-heatmap, fig.height = 4}
plot_components(fit, plot_type = "component_heatmap", type = "joint",
                block = 1L)
```

**Interpretation.** Clusters of features with consistent loading patterns
across components suggest correlated feature modules.

---

# 12  S3 autoplot / fortify — `rajive` class

## `autoplot()`

```{r s3-autoplot, fig.height = 5}
autoplot(fit)
```

---

## `fortify()`

```{r s3-fortify}
tidy_fit <- fortify(fit)
cat("Columns:", names(tidy_fit), "\n")
head(tidy_fit, 3)
```

**Interpretation.** One row per sample per joint component. Suitable for
direct use in `ggplot2` and `dplyr` without manual reshaping.

---

# 13  Feature Ranking Suite

## `rank_features()` — `"top_loadings"`

```{r rank-top}
top20 <- rank_features(fit, mode = "top_loadings", type = "joint",
                       block = 1L, component = 1L, n = 20L, signed = TRUE)
knitr::kable(head(top20, 10), digits = 4,
             caption = "Top 10 features — Block 1, Joint Component 1")
```

**Interpretation.** High absolute loading = strong driver of joint variation in
this block. Use `jackstraw_rajive()` for formal significance.

---

## `rank_features()` — `"contribution"`

```{r rank-contrib}
contrib <- rank_features(fit, mode = "contribution", type = "joint",
                         block = 1L, component = 1L)
knitr::kable(head(contrib, 8), digits = 4,
             caption = "Feature contributions (top 8)")
```

---

## `rank_features()` — `"overlap"`

```{r rank-overlap}
overlap <- rank_features(fit, mode = "overlap", type = "joint",
                         component = 1L, n = 50L, method = "jaccard")
knitr::kable(overlap, digits = 3,
             caption = "Jaccard overlap of top-50 joint features")
```

**Interpretation.** Values near 1: same features highly ranked in both blocks.
Moderate overlap (~0.2-0.4) is typical for real multi-omics data.

---

### Wrappers: `get_top_loadings()`, `get_feature_contributions()`, `compare_feature_sets_across_blocks()`

```{r rank-wrappers}
top_w     <- get_top_loadings(fit, block = 1L, component = 1L, n = 5L)
overlap_w <- compare_feature_sets_across_blocks(fit, component = 1L,
                                                n = 50L, method = "jaccard")
cat("get_top_loadings — first row:\n"); print(top_w[1, ])
cat("compare_feature_sets_across_blocks:\n"); print(overlap_w)
```

---

# 14  Association Testing Suite

## `associate_components()` — `"categorical"`

```{r assoc-cat}
knitr::kable(assoc_cat, digits = 4,
             caption = "Joint factor — group association (Kruskal-Wallis)")
```

> **Exploratory-inference caveat.** P-values are from estimated scores and do
> not propagate score estimation error. Treat as hypothesis-generating only.

---

## `associate_components()` — `"continuous"`

```{r assoc-cont}
knitr::kable(assoc_cont, digits = 4,
             caption = "Joint factor — continuous association (Pearson)")
```

---

## `associate_components()` — `"survival"` (requires *survival*)

```{r assoc-survival, eval = requireNamespace("survival", quietly = TRUE)}
assoc_surv <- associate_components(
  fit, meta_df,
  mode       = "survival",
  time_col   = "time_event",
  status_col = "event_flag",
  split      = "median"
)
knitr::kable(assoc_surv, digits = 4,
             caption = "Joint factor — survival association (log-rank, median split)")
```

> **Survival-split note.** The median-split log-rank test is descriptive. For
> primary inference prefer `split = "none"` (continuous Cox regression).

---

## `plot_components()` — `"association"`

```{r assoc-plot, fig.height = 4}
assoc_all <- rbind(assoc_cat, assoc_cont)
plot_components(assoc_results = assoc_all, plot_type = "association")
```

---

### Wrappers: `associate_scores_continuous()`, `associate_scores_categorical()`

```{r assoc-wrappers}
cont_w <- associate_scores_continuous(fit, meta_df, variable = "score_cont")
cat("Same as associate_components(mode='continuous'):\n")
print(cont_w[1:2, ])
```

---

# 15  Stability Assessment Suite

## `assess_stability()` — `"joint_rank"`

```{r stab-rank}
cat("Bootstrap joint rank distribution (B=5):\n")
print(stab_rank$rank_table)
cat("Observed rank:", stab_rank$observed_rank, "\n")
```

**Interpretation.** A concentrated distribution (all resamples returning the
same rank) indicates high rank stability.

---

## `assess_stability()` — `"loadings"`

```{r stab-loadings}
for (k in seq_along(stab_load))
  cat(sprintf("  %s: %s\n", names(stab_load)[k],
              paste(round(stab_load[[k]]$cos_similarity, 3), collapse = ", ")))
```

> **Procrustes note.** Bootstrap loadings are aligned via orthogonal Procrustes
> rotation before comparing cosine similarities. Cosine > 0.9 is typically
> considered stable.

---

## `assess_stability()` — `"components"`

```{r stab-components}
knitr::kable(stab_comp, digits = 3,
             caption = "Bootstrap stability of joint scores (B=5)")
```

---

## `plot_stability_heatmap()` / `plot_components(plot_type = "stability")`

```{r stab-heatmap, fig.height = 4}
plot_stability_heatmap(stab_load)
```

```{r stab-via-plot-components, fig.height = 4}
plot_components(stability_result = stab_load, plot_type = "stability")
```

---

### Wrappers: `bootstrap_joint_rank()`, `bootstrap_loading_stability()`

```{r stab-wrappers, eval = FALSE}
rank_draws <- bootstrap_joint_rank(blocks, c(5L, 4L, 4L), B = 5L)
load_stab  <- bootstrap_loading_stability(fit, blocks, c(5L, 4L, 4L), B = 5L)
```

---

# 16  Summarization Suite

## `summarize_components()` — `"components"`

```{r summ-components}
knitr::kable(summarize_components(fit, summary_type = "components"),
             caption = "Component catalog")
```

---

## `summarize_components()` — `"variance"`

```{r summ-variance}
knitr::kable(
  summarize_components(fit, blocks = blocks, summary_type = "variance"),
  digits = 3,
  caption = "Variance decomposition per block"
)
```

---

## `summarize_components()` — `"associations"`

```{r summ-assoc}
knitr::kable(
  summarize_components(assoc_results = assoc_all, summary_type = "associations"),
  digits = 4,
  caption = "Association summary"
)
```

---

## `summarize_components()` — `"diagnostics"`

```{r summ-diagnostics}
knitr::kable(head(summarize_components(fit, summary_type = "diagnostics"), 6),
             digits = 4, caption = "Rank diagnostics (first 6 rows)")
```

---

## `summarize_components()` — `"stability"`

```{r summ-stability}
knitr::kable(
  summarize_components(stability_result = stab_rank, summary_type = "stability"),
  digits = 3, caption = "Bootstrap joint rank distribution"
)
```

---

## `summarize_components()` — `"significance"`

```{r summ-significance}
knitr::kable(
  summarize_components(jackstraw_result = js, summary_type = "significance"),
  digits = 4, caption = "Significant features per block x component"
)
```

---

# 17  Jackstraw Significance Testing

## `jackstraw_rajive()`

```{r jack-run, eval = FALSE}
set.seed(42)
js <- jackstraw_rajive(
  ajive_output = fit,
  blocks       = blocks,
  alpha        = 0.05,
  n_null       = 5L,       # use >= 100 in practice
  correction   = "BH"
)
```

> **Significance note.** Identifies features *associated with* the estimated
> joint score — an approximation (decomposition is not re-estimated after
> feature masking). Do not interpret as causal drivers.

---

## `print.jackstraw_rajive()` / `summary.jackstraw_rajive()`

```{r jack-print-summary}
print(js)
summary(js)
```

---

## `autoplot.jackstraw_rajive()` / `fortify.jackstraw_rajive()`

```{r jack-autoplot, fig.height = 4}
autoplot(js)
```

```{r jack-fortify}
tidy_js <- fortify(js)
cat("Columns:", names(tidy_js), "\n")
head(tidy_js, 4)
```

---

## `plot_jackstraw()` — `"pvalue_hist"`

```{r jack-pvhist, fig.height = 4}
plot_jackstraw(js, type = "pvalue_hist", block = 1L, component = 1L)
```

**Interpretation.** A spike near 0 followed by a near-uniform distribution
indicates well-calibrated test with true signal. Fully uniform = no significant
features.

---

## `plot_jackstraw()` — `"scatter"`

```{r jack-scatter, fig.height = 4}
plot_jackstraw(js, type = "scatter", block = 1L, component = 1L,
               label_top = 5L)
```

---

## `plot_jackstraw()` — `"loadings_significance"`

```{r jack-load-sig, fig.height = 4}
plot_jackstraw(js, type = "loadings_significance", block = 1L)
```

---

## `plot_components()` — `"volcano"` / `"jackstraw_summary"`

```{r jack-volcano, fig.height = 4}
plot_components(jackstraw_result = js, plot_type = "volcano",
                block = 1L, component = 1L)
```

```{r jack-summary-plot, fig.height = 4}
plot_components(jackstraw_result = js, plot_type = "jackstraw_summary")
```

---

## `get_significant_vars()` / `summarize_significant_vars()`

```{r jack-sig-vars}
sig_b1c1 <- get_significant_vars(js, block = 1L, component = 1L)
cat("Significant features (block 1, component 1):", nrow(sig_b1c1), "\n")
if (nrow(sig_b1c1) > 0)
  knitr::kable(head(sig_b1c1, 8), digits = 4)
```

```{r jack-rank-sig}
sig_all <- summarize_significant_vars(js)
knitr::kable(head(sig_all, 8), digits = 4,
             caption = "All significant features (all blocks x components)")
```

---

# 18  Reporting and Export

## `export_results()` — `"csv"` / `"rds"`

```{r export-csv}
top_feats <- rank_features(fit, mode = "top_loadings", type = "joint",
                           block = 1L, component = 1L, n = 20L)
tmp_csv <- tempfile(fileext = ".csv")
export_results(top_feats, path = tmp_csv, format = "csv")
rt <- read.csv(tmp_csv)
cat("Round-trip rows/cols:", nrow(rt), "/", ncol(rt), "\n")
```

```{r export-rds}
tmp_rds <- tempfile(fileext = ".rds")
export_results(fit, path = tmp_rds, format = "rds")
fit2 <- readRDS(tmp_rds)
cat("Reloaded joint rank:", get_joint_rank(fit2), "\n")
```

---

## `rajive_report()`

```{r report-rajive}
tmp_html <- tempfile(fileext = ".html")
rajive_report(
  ajive_output     = fit,
  blocks           = blocks,
  metadata         = meta_df,
  jackstraw_result = js,
  output_file      = tmp_html,
  sections         = c("overview", "variance", "features",
                       "associations", "stability")
)
cat("Report written to:", tmp_html, "\n")
cat("File size (bytes):", file.info(tmp_html)$size, "\n")
```

**Interpretation.** A self-contained HTML starting-point deliverable. For
publication-quality outputs, use the specialized functions demonstrated above.

---

# 19  Appendix — Wrapper Quick Reference

| Wrapper | Equivalent underlying call |
|---|---|
| `get_top_loadings(fit, block=1, component=1)` | `rank_features(fit, mode="top_loadings", block=1, component=1)` |
| `get_feature_contributions(fit, block=1)` | `rank_features(fit, mode="contribution", block=1)` |
| `compare_feature_sets_across_blocks(fit, n=50)` | `rank_features(fit, mode="overlap", n=50)` |
| `summarize_significant_vars(js)` | `rank_features(jackstraw_result=js, mode="significant")` |
| `associate_scores_continuous(fit, meta, variable="x")` | `associate_components(fit, meta, variable="x", mode="continuous")` |
| `associate_scores_categorical(fit, meta, variable="g")` | `associate_components(fit, meta, variable="g", mode="categorical")` |
| `associate_scores_survival(fit, meta, time_col="t", status_col="e")` | `associate_components(fit, meta, mode="survival", time_col="t", status_col="e")` |
| `bootstrap_joint_rank(blocks, ranks, B=5)` | `assess_stability(blocks=blocks, initial_signal_ranks=ranks, target="joint_rank", B=5)` |
| `bootstrap_loading_stability(fit, blocks, ranks, B=5)` | `assess_stability(fit, blocks, ranks, target="loadings", B=5)` |
| `plot_stability_heatmap(stab_load)` | `plot_components(stability_result=stab_load, plot_type="stability")` |

---

## Session Info

```{r session-info}
sessionInfo()
```
